Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-02-05 paper.qmd
Updated Figure 17

imge_error_sample_inside <- pixels_gathered_inside |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  ggtitle("(e)") +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0.31))

```{r}
#| label: fig-model-error-mnist
#| fig-cap: "The $10\\text{-}D$ model error in \\gD{} layout of the MNIST digit 1 data shows a pattern. Most low model errors are distributed along the big non-linear cluster, while most large model errors are distributed along the small cluster. The images associated with large model errors shows different patterns of digit 1, some inside (e) the non-linear structure and others outside (d). Along the non-linear cluster, the angle of digit 1 changes (a-c)."
#| fig-pos: H
#| fig-width: 10
#| fig-height: 5
#| out-width: 80%

highd_error_2d_mnist + (right_top_img / middle_img / right_bottom_img / imge_error_sample_outside) / imge_error_sample_inside
```

>>>>

imge_error_sample_inside <- pixels_gathered_inside |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  ggtitle("(e)") +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0))

```{r}
#| label: fig-model-error-mnist
#| fig-cap: "The $10\\text{-}D$ model error in \\gD{} layout of the MNIST digit 1 data shows a pattern. Most low model errors are distributed along the big non-linear cluster, while most large model errors are distributed along the small cluster. The images associated with large model errors shows different patterns of digit 1, some inside (e) the non-linear structure and others outside (d). Along the non-linear cluster, the angle of digit 1 changes (a-c)."
#| fig-pos: H
#| fig-width: 10
#| fig-height: 10
#| out-width: 90%

# Define your current layout
top_layout <- right_top_img / middle_img / right_bottom_img / imge_error_sample_outside
full_layout <- highd_error_2d_mnist + top_layout

# Add the new full-width bottom row
final_layout <- full_layout / imge_error_sample_inside

# Display the final combined plot
final_layout
```
